P.berghei pir analysis

### 2021-09-13 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
expand stacked_barchart functionality

```{r load_packages, include = FALSE, message = FALSE}
library('readxl')
library('readr')
library('dplyr')
library('purrr')
library('ggplot2')
library("RColorBrewer")
library('colorspace')
library('data.table')
library('gridExtra')
library('tibble')
library('scales')
library('stringr')
library('viridis')
library('corrplot')
library('reshape2')
library('circlize') # for circular plots
library('plotly')
library('ComplexHeatmap')

@@

```{r stacked_barchart}
sd_bars <- TRUE
g <- stacked_barchart(melted_tpm,
                      stack_group_name = 'SorL',
                      sd_bars = sd_bars)

if(global_save_var){
ggsave('plots/thesis_chapter3_figure_stackedBarChartTPM_SorL_standevError.png',
       width = 7,
       height = 5,
       units = "in",
       g)
}

@@

# figure2binset

```{r stack_bar_graph_SorL_lowexpression-figure2binset}
#Include all stages expressed lower than a certain amount

low_express <- tpm_data_SorL_stackgenes %>% 
  group_by(stage) %>% 
  summarise(sum_tpm = sum(mean_sum_tpm)) %>% 
  filter(sum_tpm < 350)

#Calculate the range for the y value to make it look nicer

stacked_max <- max(low_express$sum_tpm)

max_tpm <- c(
  seq(
    0,
    mround(
      stacked_max,
      100),
    length.out = 11)
)

tpm_data_SorL_stackgenes_low <- filter(tpm_data_SorL_stackgenes,
                                       stage %in% low_express$stage)

y <- ggplot(data = tpm_data_SorL_stackgenes_low, 
              aes(
                x = stage_num,
                y = mean_sum_tpm, 
                fill = SorL
              )) +
    geom_bar(position = position_stack(),
             stat = 'identity',
             colour = 'black',
             size = 0.1) +
    {if(sd_bars)list(
      geom_errorbar(aes(ymax = sd_upper,
                        ymin = sd_lower),
                    position = position_dodge(width = .85),
                    size = .25),
        geom_point(aes(y = stacked_mean), 
                   position = position_dodge(width = .85),
                   show.legend = FALSE,
                   size = .25)
    )}+ 
    scale_fill_manual(
      breaks = unique(tpm_data_SorL_stackgenes$SorL),
      values = c(
        SorL_col_num,
        fills
      )
    ) +
    scale_color_manual('black') + 
    scale_y_continuous(breaks = max_tpm) +
    theme_classic() +
    ylab(
      bquote('total '~italic(.('pir'))~' TPM')
    ) +
    scale_x_continuous(
      breaks = tpm_data_SorL_stackgenes$stage_num %>% unique(),
      labels = tpm_data_SorL_stackgenes$stage %>% unique(),
      expand = c(0, 0)
    ) +
    theme(
      axis.text.x = element_text(angle = 90, 
                                 vjust = .5,
                                 size = 10),
      axis.text.y = element_text(size = 10),
      axis.title.y = element_text(size = 10),
      legend.title = element_text(size = 12),
      legend.text = element_text(size = 10),
      legend.key.size = unit(3,'mm'),
      legend.key.width = unit(2,'mm'),
    ) +
    xlab('stage') + 
    facet_grid(.~stage, 
               scales = "free_x",
               space = "free_x") +
      scale_x_discrete(expand=expand_scale(add=1)) +
    theme(
      axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 10),
      axis.title.y = element_text(size = 10),
      legend.title = element_text(size = 12),
      legend.text = element_text(size = 10),
      legend.key.size = unit(3,'mm'),
      legend.key.width = unit(2,'mm'),
      strip.text.x = element_text(size=8, 
                                  face = 'bold', 
                                  angle = 90),
      strip.background = element_rect(
        color="black", 
        size=0.1, 
        linetype="solid"
      ),
      panel.spacing.x = unit(0, "null")
    )

g <- ggplot_gtable(ggplot_build(y))
strip_t <- which(grepl('strip-t', g$layout$name))
stage_vec <- unique(
  levels(tpm_data_SorL_stackgenes_low$stage)[levels(tpm_data_SorL_stackgenes_low$stage) %in% as.character(tpm_data_SorL_stackgenes_low$stage)]
)
fills <- case_when(str_detect(stage_vec, pattern = 'Asex') ~ 'coral1' ,
                   str_detect(stage_vec, pattern = 'Liv') ~ 'plum2',
                   str_detect(stage_vec, pattern = 'Gam') ~ 'lightskyblue1',
                   str_detect(stage_vec, pattern  = 'Bld|Sporo|Ook') ~ 'lightgreen')
k <- 1
for (i in strip_t) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
grid.newpage()
grid.draw(g)
```

```{r table_of_SorL_highest_supptable}
#For a neat table
SorL_kable_index <- rep.int(2, 
                            times = length(unique(tpm_data_SorL_stackgenes$stage)))
names(SorL_kable_index) <- levels(tpm_data_SorL_stackgenes$stage)

tpm_data_SorL_stackgenes_top_table <- tpm_data_SorL_stackgenes %>% 
  mutate(Geneid = stack_group) %>% 
  filter(str_detect(SorL, 
                    pattern = 'ancestral', 
                    negate = TRUE)) %>% 
  group_by(stage) %>% 
  mutate(sum_tpm = sum(total_tpm)) %>% 
  group_by(stage, 
           SorL) %>% 
  slice_max(order_by = total_tpm,
            n = 1) %>% 
  mutate(total_tpm = round(total_tpm, digits = 2),
         prop_tpm = round(total_tpm/sum_tpm, digits = 2)) %>% 
  select(stage, Geneid, SorL, total_tpm, prop_tpm)

>>>>

```{r load_packages, include = FALSE, message = FALSE}
library('readxl')
library('readr')
library('dplyr')
library('purrr')
library('ggplot2')
library("RColorBrewer")
library('colorspace')
library('data.table')
library('gridExtra')
library('tibble')
library('scales')
library('stringr')
library('viridis')
library('corrplot')
library('reshape2')
library('circlize') # for circular plots
library('plotly')
library('ComplexHeatmap')
library('kableExtra')

@@

```{r stacked_barchart}
sd_bars <- TRUE
g_list <- stacked_barchart(melted_tpm,
                           stack_group_name = 'SorL',
                           sd_bars = sd_bars,
                           inset = TRUE)

if(global_save_var){
  ggsave('plots/thesis_chapter3_figure_stackedBarChartTPM_SorL_standevError.png',
         width = 7,
         height = 5,
         units = "in",
         g_list$main)
  ggsave('plots/thesis_chapter3_figure_stackedBarChartTPM_SorL_standevError_inset.png',
         width = 7,
         height = 5,
         units = "in",
         g_list$inset)
}

@@

```{r table_of_SorL_highest_supptable}
tpm_data_SorL_stackgenes <- g_list$data

#For a neat table
SorL_kable_index <- rep.int(2, 
                            times = length(unique(tpm_data_SorL_stackgenes$stage)))
names(SorL_kable_index) <- levels(tpm_data_SorL_stackgenes$stage)

tpm_data_SorL_stackgenes_top_table <- tpm_data_SorL_stackgenes %>% 
  mutate(Geneid = stack_group) %>% 
  filter(str_detect(SorL, 
                    pattern = 'ancestral', 
                    negate = TRUE)) %>% 
  group_by(stage) %>% 
  mutate(sum_tpm = sum(mean_sum_tpm)) %>% 
  group_by(stage, 
           SorL) %>% 
  slice_max(order_by = mean_sum_tpm,
            n = 1) %>% 
  mutate(mean_sum_tpm = round(mean_sum_tpm, digits = 2),
         prop_tpm = round(mean_sum_tpm/sum_tpm, digits = 2)) %>% 
  select(stage, Geneid, SorL, mean_sum_tpm, prop_tpm)
